Solar jet observed at the limb in SDO/SST

### 2016-07-28 paper/ms_temp_paper.tex
Add the doppler figure

>>>>

\begin{pycode}[doppler]
import sunpy
from sunpy.image import slit

import matplotlib as mpl
import matplotlib.pyplot as plt
from matplotlib import colors
from mpl_toolkits.axes_grid1 import ImageGrid
from matplotlib import gridspec
from matplotlib.collections import LineCollection

import numpy as np

import astropy.units as u
import datetime
from datetime import timedelta
from astropy.constants import c
from glob import glob

path_dop_1 = manager.data_file('dops/dop_arr_test075.npy')
path_dop_2 = manager.data_file('dops/dop_arr_test076.npy')
path_dop_3 = manager.data_file('dops/dop_arr_test077.npy')
path_dop_4 = manager.data_file('dops/dop_arr_test078.npy')
path_dop_5 = manager.data_file('dops/dop_arr_test079.npy')
path_dop_6 = manager.data_file('dops/dop_arr_test080.npy')
path_dop_7 = manager.data_file('dops/dop_arr_test081.npy')
path_dop_8 = manager.data_file('dops/dop_arr_test082.npy')
path_dop_9 = manager.data_file('dops/dop_arr_test083.npy')
path_dop_10 = manager.data_file('dops/dop_arr_test084.npy')
path_dop_11 = manager.data_file('dops/dop_arr_test085.npy')
path_dop_12 = manager.data_file('dops/dop_arr_test086.npy')
path_dop_13 = manager.data_file('dops/dop_arr_test087.npy')
path_dop_14 = manager.data_file('dops/dop_arr_test088.npy')
path_dop_15 = manager.data_file('dops/dop_arr_test089.npy')
path_dop_16 = manager.data_file('dops/dop_arr_test090.npy')

# some functions
def get_time(ind, time_0):
    current_time = time_0 + timedelta(seconds=7.7)*ind
    return current_time

def truncate_colormap(cmap, minval=0.0, maxval=1.0, n=100):
    new_cmap = colors.LinearSegmentedColormap.from_list(
        'trunc({n},{a:.2f},{b:.2f})'.format(n=cmap.name, a=minval, b=maxval),
        cmap(np.linspace(minval, maxval, n)))
    return new_cmap

# read in some datas
dop_files = []
for i in range(75,90):
	dop_files.append(manager.data_file('dops/dop_arr_test0{}.npy'.format(i)))
dop_files.sort()

t0_ha = datetime.datetime(2012,6,21,7,15,9)
t0_dop = get_time(100, t0_ha)

dops = np.zeros((len(dop_files), 331, 120))
for i, afile in enumerate(dop_files):
    dops[i] = np.load(afile)

# process the the dops to get vels
l0 = 6562.8*u.Angstrom
dops = dops*u.Angstrom
dops = (l0-dops)/l0*c
dops = dops.to(u.km/u.s)

# get the variables for the slit analysis
# lets use a perfectly horizontal slit
x1 = 45
x2 = 90
y1 = 58
y2 = 90
N = 0

dop_frames = [75,76,77,78,79,80,81,82,83]

### make the graph for time and slit
slit_inds = slit.slit_count(45, 90, 58, 90, 0, 1, N)

# index the arrays properly
inds_x = np.array([slit_inds[:,:,0]])
inds_y = np.array([slit_inds[:,:,1]])
ind_dop = dops[inds_x, inds_y, :]

dop_fin = ind_dop[0]

# get the dopplergrams associated with the rotation
slit_list = []
frames = range(79,90)
for i, n in enumerate(frames):
    temp = dop_fin[0,:,n]
    temp = temp[temp < 10*dop_fin.unit]
    slit_list.append(temp)

xy_slit = [np.array(zip(range(len(slit_inds[0])), s.value)) for s in slit_list]

slit_line =  mpl.lines.Line2D(np.array([45,58]),
                                     np.array([90,90]),
                                     linestyle='solid', color='k')

n_cmap = truncate_colormap(plt.get_cmap('Oranges'), 0.3, 1.0)

# new figure using subplot2grid specificially
fig = plt.figure(figsize=(6,12))
gs = gridspec.GridSpec(3,4)
ax1 = plt.subplot(gs[0,0])
ax2 = plt.subplot(gs[0,1])
ax3 = plt.subplot(gs[0,2])
ax4 = plt.subplot(gs[0,3])
ax5 = plt.subplot(gs[1,0])
ax6 = plt.subplot(gs[1,1])
ax7 = plt.subplot(gs[1,2])
ax8 = plt.subplot(gs[1,3])
ax9 = plt.subplot(gs[2,0])
ax10 = plt.subplot(gs[2,1:])

ax_list = [ax1, ax2, ax3, ax4, ax5,
           ax6, ax7, ax8, ax9]

for i, an_ax in zip(dop_frames, ax_list):
    temp_dop = dops[i].value
    im = an_ax.imshow(temp_dop[:250,40:], vmax=15, vmin=-15,
             cmap='RdBu', origin='lower',
             norm=mpl.colors.SymLogNorm(1))
    im.cmap.set_under('w')
    im.cmap.set_over('w')

cb = fig.colorbar(im)
cb.set_label('Velocity {}'.format(dop_fin.unit))

# line collection section
n_cmap = truncate_colormap(plt.get_cmap('Oranges'), 0.3, 1.0)

# fig, ax = plt.subplots()
line_segments = LineCollection(xy_slit,
                               linewidths = 0.25,
                               linestyle='solid',
                               cmap=n_cmap)

line_segments.set_array(np.arange(len(slit_list)))
ax10.add_collection(line_segments)
ax10.axis([1,10,-1.5,1.5])

ax4.add_line(slit_line)

axcb = fig.colorbar(line_segments)
axcb.set_label('Time')
ax10.set_title('Slit across')
ax10.set_xlabel('Distance across slit')
ax10.set_ylabel('Velocity {}'.format(dop_fin.unit))
plt.sci(line_segments)
plt.draw()
plt.show()
